Allee Effect in Cultural Evolution

### 2015-10-01 manuscript/draft.tex
title

\title{Allee Effect and Cultural Evolution}

@@

\address[label1]{CaSEs - Complexity and Socio-Ecological Dynamics Research Group, Barcelona}
\address[label2]{UCL Institute of Archaeology}
\address[label3]{BSC - Barcelona Supercomputing Center}

>>>>

\title{Allee Effect in Cultural Evolution}

@@

\address[label1]{CaSEs - Complexity and Socio-Ecological Dynamics Research Group, Universitat Pompeu Fabra, Barcelona}
\address[label2]{UCL Institute of Archaeology}
\address[label3]{CASE - Computer Applications in Science and Engineering, Barcelona Supercomputing Center}
